Verifying Spatial Properties of Stencil Computations

### 2016-11-16 paper.tex
Intro to definition is subsumed by the definition
Simplify index scheme index relationship explanation

Indexing schemes abstract array subscripts.
Our model represents the meaning of stencil specifications
as indexing schemes, which explain the range of possible
indexing behaviours which are consistent with the specification.
The relationship between source language
terms and index schemes
 is given precisely by the following function \textsf{schematic},
 which forms part of checking and inference (\Cref{sec:analysis}).

@@

The notion of which dimensions $i$ have \emph{any scheme in the model
where $u_i \neq \infty$} is represented by following  function:
\begin{definition}%[Constrained dimensions]
For an $n$-dimensional model $M$, its \emph{constrained dimensions}
are the set of dimension identifiers where at least one scheme $u \in M$ has
a non-$\infty$ value in that dimension:
%
\begin{align*}
\effdims{M}{n} =
\bigcup_{u \in M} \{i \mid i \in \{1,\ldots,n\} \, \wedge \, u_i \neq
  \infty\}
\end{align*}
For example, $\effdims{\{\vtwoh{0}{\infty},\vtwoh{\infty}{\infty}\}}{2}
 = \{1\}$.
\end{definition}
\begin{definition}The tensor $\otimes_n$ of $n$-dimensional
models is:
\begin{alignat*}{2}
& M \otimes_n N =
  \Bigg\{x \; \Bigg| \;
    \parbox{5.2cm}{$(u, v) \in M \times N,$ \\[0.1em]
                  $\;\; i \in \{1, \ldots, 2^n\}, \,
                  x = (u \bowtie v)_i,$ \\[0.1em]
                  $\;\; j \in (\effdims{M}{n} \cup
                   \effdims{N}{n}),$\\[0.1em]
                   $\;\; x_j \neq \infty$
                  } \Bigg\}
\end{alignat*}
The first guard takes the Cartesian product of
the models and quantifies over all pairings $(u, v)$.
The second guard binds $j$ which ranges over the constrained
dimensions for $M$ unioned with the constrained dimensions for $N$.
That is, every $j$ corresponds to a dimension in which
either $M$ or $N$ has a scheme $u$ where $u_j \neq \infty$,
and thus is constrained.
The \emph{pairwise permutation} $u \bowtie v$
builds a $2^n \times n$ matrix
of all possible $n$-vectors generated by
non-deterministically picking for each $j^{th}$ entry either
$u_j$ or $v_j$ \eg{}
%
\begin{equation*}
\vthreeh{0}{1}{2} \bowtie \vthreeh{3}{4}{5} =
\left[
\setlength{\arraycolsep}{0.42em}
\begin{array}{cccccccc}
0 & 0 & 0 & 0 & 3 & 3 & 3 & 3 \\
1 & 1 & 4 & 4 & 1 & 1 & 4 & 4 \\
2 & 5 & 2 & 5 & 2 & 5 & 2 & 5
\end{array}
\right]
\end{equation*}
%
The $2^n$ unique choices for $\bowtie$ on $n$-vectors
correspond to taking all bit-strings of length $n$ and
selecting from $u$ for $1$ and $v$ for $0$. The pairwise permutation
matrix is thus defined in terms of the logical
matrix $b$ where $b_{i,j}$ is the $j$-th bit of the integer
$i - 1$ as:
%
\begin{align*}
(u \bowtie v)_{i,j} & = b_{i,j} u_j + \neg b_{i,j} v_j
\end{align*}
%
The permuted schemes $x = (u \bowtie v)_i$ added to the model
$M \otimes N$ are only those without $\infty$ in
the constrained dimensions given by each model ($x_j \neq
\infty$). This eliminates all permutations with
$\infty$ in a constrained dimension position.
\end{definition}

>>>>

Indexing schemes abstract array subscripts.
Our model, consisting index schemes, explain the range of possible
indexing behaviours which are consistent with the specification.
The relationship between source language
and index schemes
 is defined by \textsf{schematic} function,
 which forms part of checking and inference (\Cref{sec:analysis}).

@@

\begin{definition}%[Constrained dimensions]
For an $n$-dimensional model $M$, its \emph{constrained dimensions}
are the set of dimension identifiers where at least one scheme $u \in M$ has
a non-$\infty$ value in that dimension:
%
\begin{align*}
\effdims{M}{n} =
\bigcup_{u \in M} \{i \mid i \in \{1,\ldots,n\} \, \wedge \, u_i \neq
  \infty\}
\end{align*}
For example, $\effdims{\{\vtwoh{0}{\infty},\vtwoh{\infty}{\infty}\}}{2}
 = \{1\}$.
\end{definition}
\begin{definition}The tensor $\otimes_n$ of $n$-dimensional
models is:
\begin{alignat*}{2}
& M \otimes_n N =
  \Bigg\{x \; \Bigg| \;
    \parbox{5.2cm}{$(u, v) \in M \times N,$ \\[0.1em]
                  $\;\; i \in \{1, \ldots, 2^n\}, \,
                  x = (u \bowtie v)_i,$ \\[0.1em]
                  $\;\; j \in (\effdims{M}{n} \cup
                   \effdims{N}{n}),$\\[0.1em]
                   $\;\; x_j \neq \infty$
                  } \Bigg\}
\end{alignat*}
The first guard takes the Cartesian product of
the models and quantifies over all pairings $(u, v)$.
The second guard binds $j$ which ranges over the constrained
dimensions for $M$ unioned with the constrained dimensions for $N$.
That is, every $j$ corresponds to a dimension in which
either $M$ or $N$ has a scheme $u$ where $u_j \neq \infty$,
and thus is constrained.
The \emph{pairwise permutation} $u \bowtie v$
builds a $2^n \times n$ matrix
of all possible $n$-vectors generated by
non-deterministically picking for each $j^{th}$ entry either
$u_j$ or $v_j$ \eg{}
%
\begin{equation*}
\vthreeh{0}{1}{2} \bowtie \vthreeh{3}{4}{5} =
\left[
\setlength{\arraycolsep}{0.42em}
\begin{array}{cccccccc}
0 & 0 & 0 & 0 & 3 & 3 & 3 & 3 \\
1 & 1 & 4 & 4 & 1 & 1 & 4 & 4 \\
2 & 5 & 2 & 5 & 2 & 5 & 2 & 5
\end{array}
\right]
\end{equation*}
%
The $2^n$ unique choices for $\bowtie$ on $n$-vectors
correspond to taking all bit-strings of length $n$ and
selecting from $u$ for $1$ and $v$ for $0$. The pairwise permutation
matrix is thus defined in terms of the logical
matrix $b$ where $b_{i,j}$ is the $j$-th bit of the integer
$i - 1$ as:
%
\begin{align*}
(u \bowtie v)_{i,j} & = b_{i,j} u_j + \neg b_{i,j} v_j
\end{align*}
%
The permuted schemes $x = (u \bowtie v)_i$ added to the model
$M \otimes N$ are only those without $\infty$ in
the constrained dimensions given by each model ($x_j \neq
\infty$). This eliminates all permutations with
$\infty$ in a constrained dimension position.
\end{definition}
